\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}
\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%% Redefines the elsarticle footer
%\makeatletter
%\def\ps@pprintTitle{%
% \let\@oddhead\@empty
% \let\@evenhead\@empty
% \def\@oddfoot{\it \hfill\today}%
% \let\@evenfoot\@oddfoot}
%\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Short Paper},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header


\usepackage[nomarkers]{endfloat}

\begin{document}
\begin{frontmatter}

  \title{Short Paper}
    \author[Some Institute of Technology]{Alice Anonymous\corref{c1}}
   \ead{alice@example.com} 
   \cortext[c1]{Corresponding Author}
    \author[Another University]{Bob Security}
   \ead{bob@example.com} 
  
      \address[Some Institute of Technology]{Department, Street, City, State, Zip}
    \address[Another University]{Department, Street, City, State, Zip}
  
  \begin{abstract}
  This is the abstract.
  
  It consists of two paragraphs.
  \end{abstract}
  
 \end{frontmatter}

\emph{Text based on elsarticle sample manuscript, see
\url{http://www.elsevier.com/author-schemas/latex-instructions\#elsarticle}}

\section{The Elsevier article class}\label{the-elsevier-article-class}

\paragraph{Installation}\label{installation}

If the document class \emph{elsarticle} is not available on your
computer, you can download and install the system package
\emph{texlive-publishers} (Linux) or install the LaTeX~package
\emph{elsarticle} using the package manager of your TeX~installation,
which is typically TeX~Live or MikTeX.(Basu et al. 2016; {\textbf{???}};
Dong et al. 2012; {\textbf{???}}; Hobbs, Thall, and Lin 2016)

\paragraph{Usage}\label{usage}

Once the package is properly installed, you can use the document class
\emph{elsarticle} to create a manuscript. Please make sure that your
manuscript follows the guidelines in the Guide for Authors of the
relevant journal. It is not necessary to typeset your manuscript in
exactly the same way as an article, unless you are submitting to a
camera-ready copy (CRC) journal.

\paragraph{Functionality}\label{functionality}

The Elsevier article class is based on the standard article class and
supports almost all of the functionality of that class. In addition, it
features commands and options to format the

\begin{itemize}
\item
  document style
\item
  baselineskip
\item
  front matter
\item
  keywords and MSC codes
\item
  theorems, definitions and proofs
\item
  lables of enumerations
\item
  citation style and labeling.
\end{itemize}

\section{Front matter}\label{front-matter}

The author names and affiliations could be formatted in two ways:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
  Group the authors per affiliation.
\item
  Use footnotes to indicate the affiliations.
\end{enumerate}

See the front matter of this document for examples. You are recommended
to conform your choice to the journal you are submitting to.

\section{Bibliography styles}\label{bibliography-styles}

\begin{verbatim}
## Additional documentation is being constructed at http://nutterb.github.io/pixiedust/index.html
\end{verbatim}

\setlength{\tabcolsep}{6pt}

\begin{table}
\centering

\label{tab:unnamed-chunk-2}\begin{tabular}{lrrrr}
  \multicolumn{1}{l}{Term} & \multicolumn{1}{r}{Estimate} & \multicolumn{1}{r}{SE} & \multicolumn{1}{r}{T-statistic} & \multicolumn{1}{r}{P-value}   \\ 
 \multicolumn{1}{l}{(Intercept)} & \multicolumn{1}{r}{9.365} & \multicolumn{1}{r}{8.373} & \multicolumn{1}{r}{1.118} & \multicolumn{1}{r}{0.27}   \\ 
 \multicolumn{1}{l}{qsec} & \multicolumn{1}{r}{1.245} & \multicolumn{1}{r}{0.383} & \multicolumn{1}{r}{3.252} & \multicolumn{1}{r}{0.003}   \\ 
 \multicolumn{1}{l}{factor(am)1} & \multicolumn{1}{r}{3.151} & \multicolumn{1}{r}{1.941} & \multicolumn{1}{r}{1.624} & \multicolumn{1}{r}{0.12}   \\ 
 \multicolumn{1}{l}{wt} & \multicolumn{1}{r}{-3.926} & \multicolumn{1}{r}{0.743} & \multicolumn{1}{r}{-5.286} & \multicolumn{1}{r}{< 0.001}   \\ 
 \multicolumn{1}{l}{factor(gear)4} & \multicolumn{1}{r}{-0.268} & \multicolumn{1}{r}{1.655} & \multicolumn{1}{r}{-0.162} & \multicolumn{1}{r}{0.87}   \\ 
 \multicolumn{1}{l}{factor(gear)5} & \multicolumn{1}{r}{-0.27} & \multicolumn{1}{r}{2.063} & \multicolumn{1}{r}{-0.131} & \multicolumn{1}{r}{0.9}   \\ 

 \end{tabular}
\end{table}

There are various bibliography styles available. You can select the
style of your choice in the preamble of this document. These styles are
Elsevier styles based on standard styles like Harvard and Vancouver.
Please use BibTeX~to generate your bibliography and include DOIs
whenever available(Basu et al. 2016; {\textbf{???}}; ``An Effect Size
Measure and Bayesian Analysis of Single-Case Designs'' 2017).

Here are two sample references: Feynman and Vernon Jr. (1963; Dirac
1953).

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-noauthor_effect_nodate}{}
``An Effect Size Measure and Bayesian Analysis of Single-Case Designs.''
2017. \emph{ResearchGate}. Accessed July 13.
\url{https://www.researchgate.net/publication/260644494_An_effect_size_measure_and_Bayesian_analysis_of_single-case_designs}.

\hypertarget{ref-basu_hierarchical_2016}{}
Basu, Cynthia, Mariam A. Ahmed, Reena V. Kartha, Richard C. Brundage,
Gerald V. Raymond, James C. Cloyd, and Bradley P. Carlin. 2016. ``A
Hierarchical Bayesian Approach for Combining
Pharmacokinetic/Pharmacodynamic Modeling and Phase IIa Trial Design in
Orphan Drugs: Treating Adrenoleukodystrophy with Lorenzo's Oil.''
\emph{Journal of Biopharmaceutical Statistics} 26 (6): 1025--39.
doi:\href{https://doi.org/10.1080/10543406.2016.1226326}{10.1080/10543406.2016.1226326}.

\hypertarget{ref-Dirac1953888}{}
Dirac, P.A.M. 1953. ``The Lorentz Transformation and Absolute Time.''
\emph{Physica} 19 (1---12): 888--96.
doi:\href{https://doi.org/10.1016/S0031-8914(53)80099-6}{10.1016/S0031-8914(53)80099-6}.

\hypertarget{ref-dong_bayesian-frequentist_2012}{}
Dong, Gaohong, Weichung Joe Shih, Dirk Moore, Hui Quan, and Stephen
Marcella. 2012. ``A Bayesian-Frequentist Two-Stage Single-Arm Phase II
Clinical Trial Design.'' \emph{Statistics in Medicine} 31 (19):
2055--67. doi:\href{https://doi.org/10.1002/sim.5330}{10.1002/sim.5330}.

\hypertarget{ref-Feynman1963118}{}
Feynman, R.P, and F.L Vernon Jr. 1963. ``The Theory of a General Quantum
System Interacting with a Linear Dissipative System.'' \emph{Annals of
Physics} 24: 118--73.
doi:\href{https://doi.org/10.1016/0003-4916(63)90068-X}{10.1016/0003-4916(63)90068-X}.

\hypertarget{ref-hobbs_bayesian_2016}{}
Hobbs, Brian P., Peter F. Thall, and Steven H. Lin. 2016. ``Bayesian
Group Sequential Clinical Trial Design Using Total Toxicity Burden and
Progression-Free Survival.'' \emph{Journal of the Royal Statistical
Society. Series C, Applied Statistics} 65 (2): 273--97.
doi:\href{https://doi.org/10.1111/rssc.12117}{10.1111/rssc.12117}.

\end{document}


